rsunlight
======

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "inst/img/"
)
```

[![Build Status](https://travis-ci.org/rOpenGov/rsunlight.svg?branch=master)](https://travis-ci.org/rOpenGov/rsunlight)
[![codecov.io](https://codecov.io/github/rOpenGov/rsunlight/coverage.svg?branch=master)](https://codecov.io/github/rOpenGov/rsunlight?branch=master)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/rsunlight)](https://github.com/metacran/cranlogs.app)
[![cran version](http://www.r-pkg.org/badges/version/rsunlight)](https://cran.r-project.org/package=rsunlight)


+ Maintainer: [Scott Chamberlain](https://github.com/sckott/)
+ License: [MIT](http://opensource.org/licenses/MIT)
+ Report any problems in the [Issues Tracker](https://github.com/ropengov/rsunlight/issues), or just fork and submit changes, etc.


> NOTE: Capitol Words API is defunct

`rsunlight` is a collection of functions to search and acquire data from the various APIs that used to be housed under Sunlight Labs, but which are now housed under ProPublica.

`rsunlight` wraps functions in APIs for:

* Congress API (`cg`) - Run by ProPublica
* Open States API (`os`) - Run by OpenStates foundation

Functions that wrap these sets of APIs will be prefixed by `cg` or `os` for the different methods listed above:

* `cg` + `fxn`
* `os` + `fxn`

where `fxn` would be a function to a interface with a specific API.


You need API keys for Propublica APIs. Get them at
<https://www.propublica.org/datastore/apis>

You need an API key for the OpenStates API. Get it at
<https://openstates.org/api/register/>


We set up the functions so that you can use either env vars, or R options.
For env vars, put an entry in your `.Renviron` file with the names
`PROPUBLICA_API_KEY` and `OPEN_STATES_KEY`.

## Install rsunlight

From CRAN

```{r eval=FALSE}
install.packages("rsunlight")
```

Or development version from Github

```{r eval=FALSE}
devtools::install_github("ropengov/rsunlight")
```

```{r}
library("rsunlight")
```

## Congress API

Search for congress members by chamber and state

```{r}
cg_members_state_district('senate', 'RI')
```

Search for committees by congress and chamber

```{r}
cg_committees(115, "senate")[[1]]$committees[[1]]
```

## Open States API

Bill Search - Search for bills with the term _agriculture_, in Texas, and in the upper chamber.

```{r}
os_billsearch(terms = 'agriculture', state = 'tx', chamber = 'upper')
```

Legislator Search - Search for Republican legislators in Nevada

```{r}
os_legislatorsearch(state = 'nv', party = 'republican')
```

## Meta

* Please [report any issues or bugs](https://github.com/ropengov/rsunlight/issues).
* License: MIT
* Get citation information for `rsunlight` in R doing `citation(package = 'rsunlight')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
