<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{rsunlight vignette}
-->

rsunlight vignette - Interface to Sunlight Labs APIs.
======

### About the package

`rsunlight` is an R package to search and retrieve data from the Sunlight Labs APIs. 

Returned objects from functions are simple lists. That is, you likely will want to take output objects and make data.frames, vectors, matrices, etc. In future versions of rsunlight, I will return data.frame's when possible as those are easy to work with in R for beginners, though advanced users may prefer lists or raw responses from the API with lots of info, including header, etc.

********************

```{r keys, eval=TRUE, echo=FALSE}
sunlightkey <- getOption("SunlightLabsKey")
```

#### Install rsunlight

```{r install, eval=FALSE, echo=TRUE}
install.packages("devtools")
library('devtools')
install_github("rsunlight", "ropengov")
```

********************

#### Load rsunlight and other dependency libraries

```{r load, warning=FALSE, message=FALSE}
library('rsunlight')
```

********************

#### Gets details (subcommittees + membership) for a committee by id.

```{r cg_getcommittees, warning=FALSE, message=FALSE, cache=FALSE}
out <- cg_committees(id = 'JSPR')
head(out$results)
```

********************

#### Get districts for a latitude/longitude.

```{r cg_getdistrictlatlong, warning=FALSE, cache=FALSE}
cg_districts(latitude = 35.778788, longitude = -78.787805)
```

********************

#### Get districts that overlap for a certain zip code.

```{r cg_getdistrictzip, warning=FALSE, cache=FALSE}
cg_districts(zip = 27511)
```

********************

#### Search politicians by name

```{r cg_getlegislatorsearch, warning=FALSE, cache=FALSE}
out <- cg_legislators(last_name = 'Reed')
head(out$results)
```

********************

#### Search politicians by zip code

And get their names and Twitter handles

```{r cg_legislatorsallforzip, warning=FALSE, cache=FALSE}
out <- cg_legislators(zip = 77006)
out$results[,c('last_name','first_name','twitter_id')]
```

********************

#### Popularity of a phrase through time.

Get a list of how many times the phrase "united states" appears in the Congressional Record in each month between January and June, 2010:

```{r cw_timeseries1, warning=FALSE, cache=FALSE}
cw_timeseries(phrase='united states', start_date='2009-01-01', end_date='2009-04-30', granularity='month')
```

##### Plot data

```{r cw_timeseries2, warning=FALSE, cache=FALSE, tidy=FALSE}
library('ggplot2')
dat <- cw_timeseries(phrase='climate change')
ggplot(dat, aes(day, count)) + 
  geom_line() + 
  theme_grey(base_size=20)
```

##### Plot more data

```{r cw_timeseries3, warning=FALSE, cache=FALSE, tidy=FALSE}
dat_d <- cw_timeseries(phrase='climate change', party="D")
dat_d$party <- rep("D", nrow(dat_d))
dat_r <- cw_timeseries(phrase='climate change', party="R")
dat_r$party <- rep("R", nrow(dat_r))
dat_both <- rbind(dat_d, dat_r)
ggplot(dat_both, aes(day, count, colour=party)) + 
  geom_line() + 
  theme_grey(base_size=20) + 
  scale_colour_manual(values=c("blue","red"))
```

********************

#### Search OpenStates bills.

```{r os_billsearch, warning=FALSE, cache=FALSE}
out <- os_billsearch(terms = 'agriculture', state = 'tx', chamber = 'upper')
out$title[1:10]
```

********************

#### Search Legislators on OpenStates

```{r os_legislatorsearch, warning=FALSE, cache=FALSE}
out <- os_legislatorsearch(state = 'tx', party = 'democratic', active = TRUE)
head(out[,c('full_name','state','district')])
```

********************

#### Search for entities

That is, politicians, individuals, or organizations with the given name

```{r ts_aggregatesearch, warning=FALSE, message=FALSE, cache=FALSE}
out <- ie_entities('Nancy Pelosi')
out
```

********************

#### Contributions by industries

Return the top contributoring companies by industry, ranked by total dollars given. The `entity_id` of `ba400a177400497680cac90f678ecb8f` is the identifier for _oil and gas_.

```{r}
ie_industries(method='top_org', entity_id='ba400a177400497680cac90f678ecb8f')
```


#### Contributions by a certain amount

```{r warning=FALSE, cache=FALSE}
out <- ie_contr(recipient_state='al', for_against='for', amount='>|1000000')
out[,c('recipient_name','amount','contributor_name')]
```
